Output tables for 1xN statistical comparisons.

### 2019-03-23 Papers/SHADE/paperSHADE.tex
Resultados de DILS completos

The Biased Random-key Genetic Algorithm (BRKGA) was first proposed in \cite{gonccalves2011biased} as a variant of the RKGA. In the BRKGA optimization process, first, the population $P$ of $p_{size}$ vectors of random-keys is initialized; this will be the initial generation. Each random-key vector $p_i$ has $v$ random-keys in it. The population is sorted by the fitness value $f_i$ of each $p_i$ to select the first $p_e$ individuals, this is, the elite of the population. The elite will be preserved in the next generation without modification. To introduce diversity, a number $p_m$ of new random-keys vectors are also included in the next generation. The remaining individuals of the new generation ($p_{size} - p_e - p_m$) are obtained through crossovers between elite and non-elite parents.

@@

\begin{equation}
f_i = z_i + \overbrace{(\mu * n * {infeasibility}_i)}^{penalty},
\label{eq1}
\end{equation}

\noindent where $\mu$ is a high value, $infeasibility_i$ is the number of non-satisfied constraints and $z_i$ is the within-cluster-sum-of-squares which can be computed as in Equation \eqref{eq2}.

@@

Since SHADE is an evolution-based algorithm, it shares elements with BRKGA (Section \ref{sec:brkga}), so we will use a similar notation to define its elements. We will note the population as $P_G$, formed by $p_{size}$ individuals with the form $p_{[i,G]} = \{p_{[i,G,1]}, \cdots, p_{[i,G,v]}\}$, with $G$ indicating the generation to which $p_i$ belongs.

@@

\begin{equation}
m_{[i,G]} = p_{[i,G]} + F_i * (p_{[pbest, G]} - p_{[i,G]}) + F_i * (p_{[r1, G]} - p_{[r2,G]}),
\label{eq3}
\end{equation}

\noindent where $m_{[i,G]}$ is the mutant vector, which is generated with an individual $p_{[i,G]}$ from the population serving as a starting point. Indices $r1$ and $r2$ are random values in the range $[0,p_{size}]$, different from $i$ and from each other. The individual $p_{[pbest, G]}$ is randomly selected from among the best $p_{size} \times pbest\;|\;pbest\in [0,1]$ individuals in the population. This way, the parameter $pbest$ controls the greediness of the mutation strategy. The parameter $F_i$ defines the magnitude of the operator.

@@

\begin{equation}
t_{[i,G,j]} = \left\{ \begin{array}{lc}
m_{[i,G,j]} &   if \;\; \text{rand}[0,1) \le CR_i \;\; or \;\;j = j_{rand} \\
p_{[i,G,j]} &  \text{otherwise}
\end{array}
\right.,
\label{eq4}
\end{equation}

\noindent where $rand[0,1)$ is a random number selected from a normal distribution in the range $[0,1)$, $j_{rand}$ is a random integer selected from the range $[1,v]$, and $CR \in [0,1]$ is the crossover ratio.

The SHADE selection operator determines the survivors individuals for the next generation. It compares each parent $x_{[i,G]}$ with the trial vector $_{[i,G,j]}$, generated based on it. The best one of these two individuals will survive for the next generation. Equation \eqref{eq5} shows this concept.

\begin{equation}
p_{[i,G + 1]} = \left\{ \begin{array}{lc}
t_{[i,G]} &   if \;\; f(t_{[i,G]}) \le f(p_{[i,G]}) \\
p_{[i,G]} &  \text{otherwise}
\end{array}
\right.
\label{eq5}
\end{equation}

@@

The parameters $pbest$, $F_i$ and $CR_i$ are difficult to adjust and their selection is not trivial, as they largely determine the success of the optimization process. These are the parameters that SHADE adaptively optimizes using the mentioned history record.

@@

\noindent where $randn(\mu, \sigma^2)$ and $randc(\mu, \sigma^2)$ are random values from normal and Cauchy distributions respectively, with mean $\mu$ and variance $\sigma^2$. When a value for $CR_i$ outside of the range $[0,1]$ is generated, it is replaced by the corresponding limit value. If $F_i > 1$, then it is truncated to $1$; conversely, if $F_i < 0$, then Equation \eqref{eq7} is applied as many times as needed to obtain a legal value.

@@

\begin{equation}
M_{[CR,h,G+1]} = \left\{ \begin{array}{lc}
\text{mean}_{WA} (S_{CR}) &   if \;\; S_{CR} \neq \emptyset \\
M_{[CR,h,G]} &  otherwise
\end{array}
\right.
\label{eq8}
\end{equation}

\begin{equation}
M_{[F,h,G+1]} = \left\{ \begin{array}{lc}
\text{mean}_{WL} (S_{F}) &   if \;\; S_{F} \neq \emptyset \\
M_{[F,h,G]} &  otherwise
\end{array}
\right.
\label{eq9}
\end{equation}

@@

In Equation \ref{eq8}, the term $mean_{WA} (S_{CR})$ is the weighted mean, which is computed following Equations \eqref{eq10} and \eqref{eq11}, proposed in \cite{peng2009multi} to prevent $CR$ from converging to small values.

@@

In Equation \ref{eq9} the term $mean_{WL} (S_{F})$ refers to the weighted Lehmer mean, which is computed as in Equation \eqref{eq12} (proposed in \cite{tanabe2013success}).

@@

Unlike parameters $S_{CR}$ and $S_F$, the parameter $pbest$ from Equation \eqref{eq3}, used to set the greediness of the mutation strategy, is not included in the adaptive optimization process. However, it is not static: it is calculated for every individual $p_i$ of the population following Equation \eqref{eq13}.

\begin{equation}
pbest_i = \text{randn}[2/N, 0.2],
\label{eq13}
\end{equation}

@@

\begin{equation}
f_i = z_i * (infeasibility + 1)
\label{eq14}
\end{equation}

@@

To make these concepts clear we consider a toy dataset and three partitions over it. The dataset from Figure \ref{img:toydatasets} contains 100 instances and a single ML constraint between two instances from the same class. Partitions $C_0$---displaying the true labels---and $C_1$ do not violate the constraint ($infeasibility = 0$), whereas $C_2$ does violate it ($infeasibility = 1$). However, $C_2$ shows a possibility, for later iterations, of adding both instances to their nearest cluster while also satisfying the ML constraint.

@@

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.3}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{c c c c c c}
			\hline
			\multirow{2}{*}{Partition} &
			\multicolumn{2}{c}{Expression} &&
			\multicolumn{2}{c}{Value} \\
			\cline{2-3} \cline{5-6}
			& $f_1$ & $f_2$ && $f_1$ & $f_2$ \\
			\hline
			$C_0$ & $z_0$ & $z_0$ && $0.457$  & $0.457$  \\
			$C_1$ & $z_1$ & $z_1$ && $0.540$  & $0.540$  \\
			$C_2$ & $z_2 + (\mu * N * infs)$ & $z_2 * (infs + 1)$  && $0.503 + 1000 = 1000.503$ &  $0.503 * 2 = 1.005$ \\
			\hline

@@

\begin{equation}
Rand(C_1, C_2) = \frac{a + b}{n(n - 1)/2}
\label{eq15}
\end{equation}

@@

\begin{equation}
ARI(C_1, C_2) = \frac{Rand(C_1, C_2) - ExpectedIndex}{MaximumIndex - ExpectedIndex},
\label{eq16}
\end{equation}

\noindent where $MaximumIndex$ is expected to be 1 and $ExpectedIndex$ is the already mentioned expected degree of similarity with a random model. It is easy to see that $ARI(C_1, C_2) \in [-1,1]$, such that an $ARI$ value close to 1 means a high degree of agreement between $C_1$ and $C_2$, a positive value close to 0 means no agreement and a value smaller that 0 means that the $Rand(C_1, C_2)$ is less than expected when comparing with random partitions. To summarize, the higher the $ARI$, the greater the degree of similarity between $C_1$ and $C_2$. For more details on ARI see \cite{hubert1985comparing}.

@@

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.4}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{>{\centering\arraybackslash}c m{5cm} cc}
			\hline
			Parameter & Meaning & BRKGA & SHADE \\
			\hline
			$p_{size}$ & Population size & 100 & 100 \\
			$Evals$ & Fitness function evaluations & 300000 & 300000 \\
			$p_e$ & Size of the elite set in population & $0.2 * p_{size}$ & $0.25 * p_{size}$ \\
			$p_m$ & Number of mutants to be introduced in the population in each generation & $0.2 * p_{size}$ & - \\
			$p_{inherit}$ & Probability that a feature is inherited from an elite parent & $50\%$ & - \\
			$k$ & Output partition number of clusters & \multicolumn{2}{m{4cm}}{No. Classes (Table \ref{tab:datasets}).} \\
			\hline

@@

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.4}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{>{\centering\arraybackslash}c m{5cm} c}
			\hline
			Common Parameters & Meaning & Value \\
			\hline
			\texttt{max\_iter} & Maximum number of iterations & 300 \\
			$k$ & Output partition number of clusters & No. Classes (Table \ref{tab:datasets}). \\
			\hline
			\hline
			Specific Parameters & \multicolumn{2}{l}{Name and Value} \\
			\hline
			COPKM & \multicolumn{2}{l}{\texttt{tolerance} = $1 * 10^{-4}$; \texttt{init\_mode} = \texttt{``rand''}} \\
			CECM & \multicolumn{2}{l}{$\alpha = 1$, $\rho = 100$, $\xi = 0.5$, \texttt{stop\_threshold} = $1 * 10^{-3}$, \texttt{init\_mode} = \texttt{``rand''}} \\
			LCVQE & \multicolumn{2}{l}{\texttt{initial\_centroids} = $\emptyset$} \\
			RDPM & \multicolumn{2}{l}{$\xi_0 = 0.1$, $\xi_{rate} = 1$, $\lambda$ is calculated on the basis of the mean distances in the dataset.} \\
			TVClust & \multicolumn{2}{l}{$\alpha_0 = 1.2$, \texttt{stop\_threshold} = $5*10^{-4}$} \\
			\hline

@@

It should be noted that the study presented in this document aims to compare average performance, not peak performance. The parameter optimization process required for each algorithm and dataset falls outside the scope of this study.

@@

Furthermore, and this is a situation that all researchers have faced, NHST do not provide any information about the null hypothesis! That is: What can we conclude when NHST do not reject $H_0$? We can not infer anything since NHST can not provide evidence in its favor.

@@

The Bayesian sign test is based on obtaining the statistical distribution of a certain parameter $\rho$ according to the difference between the results, under the assumption that said distribution is a Dirichlet distribution. To get the distribution of $\rho$ we count the number of times that $A - B < 0$, the number of times where there are no significant differences, and the number of times that $A - B > 0$. In order to identify cases where there are no significant differences, we define the region of practical equivalence (rope) $[r_{min}, r_{max}]$, so that $P(A \approx B) = P(\rho \in rope)$. Using these results we calculate the weights of the Dirichlet distribution and sample it to get a set of triplets with the following form: 
$$[P(\rho < r_{min}) = P(A - B < 0),\;\; P(\rho \in rope),\;\; P(\rho > r_{max}) = P(A - B > 0)]$$

>>>>

The Biased Random-key Genetic Algorithm (BRKGA) was first proposed in \cite{gonccalves2011biased} as a variant of the RKGA. In the BRKGA optimization process, first, the population $P$ of $p_\text{size}$ vectors of random-keys is initialized; this will be the initial generation. Each random-key vector $p_i$ has $v$ random-keys in it. The population is sorted by the fitness value $f_i$ of each $p_i$ to select the first $p_e$ individuals, this is, the elite of the population. The elite will be preserved in the next generation without modification. To introduce diversity, a number $p_m$ of new random-keys vectors are also included in the next generation. The remaining individuals of the new generation ($p_\text{size} - p_e - p_m$) are obtained through crossovers between elite and non-elite parents.

@@

\begin{equation}
f_i = z_i + \overbrace{(\mu * n * \text{infeasibility}_i)}^\text{penalty},
\label{eq1}
\end{equation}

\noindent where $\mu$ is a high value, $\text{infeasibility}_i$ is the number of non-satisfied constraints and $z_i$ is the within-cluster-sum-of-squares which can be computed as in Equation \eqref{eq2}.

@@

Since SHADE is an evolution-based algorithm, it shares elements with BRKGA (Section \ref{sec:brkga}), so we will use a similar notation to define its elements. We will note the population as $P_G$, formed by $p_\text{size}$ individuals with the form $p_{[i,G]} = \{p_{[i,G,1]}, \cdots, p_{[i,G,v]}\}$, with $G$ indicating the generation to which $p_i$ belongs.

@@

\begin{equation}
m_{[i,G]} = p_{[i,G]} + F_i * (p_{[p\text{best}, G]} - p_{[i,G]}) + F_i * (p_{[r1, G]} - p_{[r2,G]}),
\label{eq3}
\end{equation}

\noindent where $m_{[i,G]}$ is the mutant vector, which is generated with an individual $p_{[i,G]}$ from the population serving as a starting point. Indices $r1$ and $r2$ are random values in the range $[0,p_\text{size}]$, different from $i$ and from each other. The individual $p_{[p\text{best}, G]}$ is randomly selected from among the best $p_\text{size} \times p\text{best}\;|\;p\text{best}\in [0,1]$ individuals in the population. This way, the parameter $p\text{best}$ controls the greediness of the mutation strategy. The parameter $F_i$ defines the magnitude of the operator.

@@

\begin{equation}
t_{[i,G,j]} = \left\{ \begin{array}{lc}
m_{[i,G,j]} &   \text{if} \;\; \text{rand}[0,1) \le CR_i \;\; \text{or} \;\;j = j_{rand} \\
p_{[i,G,j]} &  \text{otherwise}
\end{array}
\right.,
\label{eq4}
\end{equation}

\noindent where $\text{rand}[0,1)$ is a random number selected from a normal distribution in the range $[0,1)$, $j_\text{rand}$ is a random integer selected from the range $[1,v]$, and $CR \in [0,1]$ is the crossover ratio.

The SHADE selection operator determines the survivors individuals for the next generation. It compares each parent $x_{[i,G]}$ with the trial vector $t_{[i,G,j]}$, generated based on it. The best one of these two individuals will survive for the next generation. Equation \eqref{eq5} shows this concept.

\begin{equation}
p_{[i,G + 1]} = \left\{ \begin{array}{lc}
t_{[i,G]} &   \text{if} \;\; f(t_{[i,G]}) \le f(p_{[i,G]}) \\
p_{[i,G]} &  \text{otherwise}
\end{array}
\right.
\label{eq5}
\end{equation}

@@

The parameters $p\text{best}$, $F_i$ and $CR_i$ are difficult to adjust and their selection is not trivial, as they largely determine the success of the optimization process. These are the parameters that SHADE adaptively optimizes using the mentioned history record.

@@

\noindent where $\text{randn}(\mu, \sigma^2)$ and $\text{randc}(\mu, \sigma^2)$ are random values from normal and Cauchy distributions respectively, with mean $\mu$ and variance $\sigma^2$. When a value for $CR_i$ outside of the range $[0,1]$ is generated, it is replaced by the corresponding limit value. If $F_i > 1$, then it is truncated to $1$; conversely, if $F_i < 0$, then Equation \eqref{eq7} is applied as many times as needed to obtain a legal value.

@@

\begin{equation}
M_{[CR,h,G+1]} = \left\{ \begin{array}{lc}
\text{mean}_{WA} (S_{CR}) & \text{if} \;\; S_{CR} \neq \emptyset \\
M_{[CR,h,G]} &  \text{otherwise}
\end{array}
\right.
\label{eq8}
\end{equation}

\begin{equation}
M_{[F,h,G+1]} = \left\{ \begin{array}{lc}
\text{mean}_{WL} (S_{F}) & \text{if} \;\; S_{F} \neq \emptyset \\
M_{[F,h,G]} &  \text{otherwise}
\end{array}
\right.
\label{eq9}
\end{equation}

@@

In Equation \ref{eq8}, the term $\text{mean}_{WA} (S_{CR})$ is the weighted mean, which is computed following Equations \eqref{eq10} and \eqref{eq11}, proposed in \cite{peng2009multi} to prevent $CR$ from converging to small values.

@@

In Equation \ref{eq9} the term $\text{mean}_{WL} (S_{F})$ refers to the weighted Lehmer mean, which is computed as in Equation \eqref{eq12} (proposed in \cite{tanabe2013success}).

@@

Unlike parameters $S_{CR}$ and $S_F$, the parameter $p\text{best}$ from Equation \eqref{eq3}, used to set the greediness of the mutation strategy, is not included in the adaptive optimization process. However, it is not static: it is calculated for every individual $p_i$ of the population following Equation \eqref{eq13}.

\begin{equation}
p\text{best}_i = \text{randn}[2/N, 0.2],
\label{eq13}
\end{equation}

@@

\begin{equation}
f_i = z_i * (\text{infeasibility}_i + 1)
\label{eq14}
\end{equation}

@@

To make these concepts clear we consider a toy dataset and three partitions over it. The dataset from Figure \ref{img:toydatasets} contains 100 instances and a single ML constraint between two instances from the same class. Partitions $C_0$---displaying the true labels---and $C_1$ do not violate the constraint ($\text{infeasibility} = 0$), whereas $C_2$ does violate it ($\text{infeasibility} = 1$). However, $C_2$ shows a possibility, for later iterations, of adding both instances to their nearest cluster while also satisfying the ML constraint.

@@

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.3}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{c c c c c c}
			\hline
			\multirow{2}{*}{Partition} &
			\multicolumn{2}{c}{Expression} &&
			\multicolumn{2}{c}{Value} \\
			\cline{2-3} \cline{5-6}
			& $f_1$ & $f_2$ && $f_1$ & $f_2$ \\
			\hline
			$C_0$ & $z_0$ & $z_0$ && $0.457$  & $0.457$  \\
			$C_1$ & $z_1$ & $z_1$ && $0.540$  & $0.540$  \\
			$C_2$ & $z_2 + (\mu * N * \text{infsblt})$ & $z_2 * (\text{infsblt} + 1)$  && $0.503 + 1000 = 1000.503$ &  $0.503 * 2 = 1.005$ \\
			\hline

@@

\begin{equation}
\text{Rand}(C_1, C_2) = \frac{a + b}{n(n - 1)/2}
\label{eq15}
\end{equation}

@@

\begin{equation}
\text{ARI}(C_1, C_2) = \frac{\text{Rand}(C_1, C_2) - \text{Expected Index}}{\text{Maximum Index} - \text{Expected Index}},
\label{eq16}
\end{equation}

\noindent where Maximum Index is expected to be 1 and Expected Index is the already mentioned expected degree of similarity with a random model. It is easy to see that $\text{ARI}(C_1, C_2) \in [-1,1]$, such that an ARI value close to 1 means a high degree of agreement between $C_1$ and $C_2$, a positive value close to 0 means no agreement and a value smaller that 0 means that the $\text{Rand}(C_1, C_2)$ is less than expected when comparing with random partitions. To summarize, the higher the ARI, the greater the degree of similarity between $C_1$ and $C_2$. For more details on ARI see \cite{hubert1985comparing}.

@@

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.4}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{>{\centering\arraybackslash}c m{5cm} cc}
			\hline
			Parameter & Meaning & BRKGA & SHADE \\
			\hline
			$p_\text{size}$ & Population size & 100 & 100 \\
			Evals & Fitness function evaluations & 300000 & 300000 \\
			$p_e$ & Size of the elite set in population & $0.2 * p_\text{size}$ & $0.25 * p_\text{size}$ \\
			$p_m$ & Number of mutants to be introduced in the population in each generation & $0.2 * p_\text{size}$ & - \\
			$p_\text{inherit}$ & Probability that a feature is inherited from an elite parent & $50\%$ & - \\
			$k$ & Output partition number of clusters & \multicolumn{2}{m{4cm}}{No. Classes (Table \ref{tab:datasets}).} \\
			\hline

@@

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.4}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{>{\centering\arraybackslash}c m{5cm} c}
			\hline
			Common Parameters & Meaning & Value \\
			\hline
			\texttt{max\_iter} & Maximum number of iterations & 300 \\
			$k$ & Output partition number of clusters & No. Classes (Table \ref{tab:datasets}). \\
			\hline
			\hline
			Specific Parameters & \multicolumn{2}{l}{Name and Value} \\
			\hline
			COPKM & \multicolumn{2}{l}{\texttt{tolerance} = $1 * 10^{-4}$; \texttt{init\_mode} = \texttt{``rand''}} \\
			CECM & \multicolumn{2}{l}{$\alpha = 1$, $\rho = 100$, $\xi = 0.5$, \texttt{stop\_threshold} = $1 * 10^{-3}$, \texttt{init\_mode} = \texttt{``rand''}} \\
			LCVQE & \multicolumn{2}{l}{\texttt{initial\_centroids} = $\emptyset$} \\
			RDPM & \multicolumn{2}{l}{$\xi_0 = 0.1$, $\xi_\text{rate} = 1$, $\lambda$ is calculated on the basis of the mean distances in the dataset.} \\
			TVClust & \multicolumn{2}{l}{$\alpha_0 = 1.2$, \texttt{stop\_threshold} = $5*10^{-4}$} \\
			\hline

@@

Parameter values have been assigned following the guidelines of the original creators of the different proposals. Since the evaluation in the experimental stage makes use of a high number of datasets, tuning each parameter specifically for each dataset is not feasible. Indeed, our goal is not optimization in a case-by-case basis but instead a comparison in the most general scenario possible. Therefore, given that the purpose of this work is to draw a fair comparison between the algorithms and assess their robustness in a common environment with multiple datasets, we have not included a tuning step to maximize any particular performance metric.

@@

Furthermore, and this is a situation that all researchers have faced, NHST do not provide any information about the null hypothesis! That is: What can we conclude when NHST do not reject the null hypothesis? We can not infer anything since NHST can not provide evidence in its favor.

@@

The Bayesian sign test is based on obtaining the statistical distribution of a certain parameter $\rho$ according to the difference between the results, under the assumption that said distribution is a Dirichlet distribution. To get the distribution of $\rho$ we count the number of times that $A - B < 0$, the number of times where there are no significant differences, and the number of times that $A - B > 0$. In order to identify cases where there are no significant differences, we define the region of practical equivalence (rope) $[r_\text{min}, r_\text{max}]$, so that $P(A \approx B) = P(\rho \in \text{rope})$. Using these results we calculate the weights of the Dirichlet distribution and sample it to get a set of triplets with the following form: 
$$[P(\rho < r_\text{min}) = P(A - B < 0),\;\; P(\rho \in \text{rope}),\;\; P(\rho > r_\text{max}) = P(A - B > 0)]$$

### 2019-03-23 Resultados/ResultadosTFG/Friedman/Friedman15/Friedman15.tex
Resultados de DILS completos

\begin{table}[!htp]
\centering
\begin{tabular}{|c|c|}\hline
Algorithm&Ranking\\\hline
"SHADE"&3.04\\"COPKM"&4.6\\"LCVQE"&2.7\\"RDPM"&2.78\\"TVClust"&3.22\\"CEKM"&4.66\\\hline\end{tabular}
\caption{Average Rankings of the algorithms (Friedman)}
\end{table}

Friedman statistic (distributed according to chi-square with 5 degrees of freedom): 28.6. \newline P-value computed by Friedman Test: 0.000028.\newline

@@

\begin{table}[!htp]
\centering\footnotesize
\begin{tabular}{cccccccc}
$i$&algorithm&$z=(R_0 - R_i)/SE$&$p$&Holm &Holland&Finner&Li\\
\hline5&"CEKM"&3.704052&0.000212&0.01&0.010206&0.010206&0.006325\\4&"COPKM"&3.590662&0.00033&0.0125&0.012741&0.020308&0.006325\\3&"TVClust"&0.982708&0.325751&0.016667&0.016952&0.030307&0.006325\\2&"SHADE"&0.64254&0.520523&0.025&0.025321&0.040204&0.006325\\1&"RDPM"&0.151186&0.879829&0.05&0.05&0.05&0.05\\\hline
\end{tabular}
\caption{Post Hoc comparison Table for $\alpha=0.05$ (FRIEDMAN)}
\end{table}Holm's procedure rejects those hypotheses that have an unadjusted p-value $\le0.016667$.

Holland's procedure rejects those hypotheses that have an unadjusted p-value $\le0.016952$.

Finner's procedure rejects those hypotheses that have an unadjusted p-value $\le0.030307$.

Li's procedure rejects those hypotheses that have an unadjusted p-value $\le0.006325$.

@@

\begin{table}[!htp]
\centering\small
\begin{tabular}{cccc}
i&algorithm&unadjusted $p$&$p_{Holm}$\\
\hline1&"CEKM"&0.000212&0.001061\\2&"COPKM"&0.00033&0.001319\\3&"TVClust"&0.325751&0.977254\\4&"SHADE"&0.520523&1.041046\\5&"RDPM"&0.879829&1.041046\\\hline
\end{tabular}
\caption{Adjusted $p$-values (FRIEDMAN) (I)}
\end{table}
\begin{table}[!htp]
\centering\small
\begin{tabular}{cccccc}
i&algorithm&unadjusted $p$&$p_{Holland}$&$p_{Finner}$&$p_{Li}$\\
\hline1&"CEKM"&0.000212&0.00106&0.00106&0.001763\\2&"COPKM"&0.00033&0.001319&0.00106&0.002737\\3&"TVClust"&0.325751&0.693479&0.481558&0.730512\\4&"SHADE"&0.520523&0.770102&0.601012&0.812436\\5&"RDPM"&0.879829&0.879829&0.879829&0.879829\\\hline
\end{tabular}
\caption{Adjusted $p$-values (FRIEDMAN) (II)}
\end{table}

>>>>

\begin{table}[!htp]
\centering
\begin{tabular}{|c|c|}\hline
Algorithm&Ranking\\\hline
"SHADE"&2.92\\"COPKM"&3.24\\"LCVQE"&3.24\\"RDPM"&3.24\\"TVClust"&3.42\\"CEKM"&4.94\\\hline\end{tabular}
\caption{Average Rankings of the algorithms (Friedman)}
\end{table}

Friedman statistic (distributed according to chi-square with 5 degrees of freedom): 18.708571. \newline P-value computed by Friedman Test: 0.002178.\newline

@@

\begin{table}[!htp]
\centering\footnotesize
\begin{tabular}{cccccccc}
$i$&algorithm&$z=(R_0 - R_i)/SE$&$p$&Holm &Holland&Finner&Li\\
\hline5&"CEKM"&3.817441&0.000135&0.01&0.010206&0.010206&0.023929\\4&"TVClust"&0.944911&0.344704&0.0125&0.012741&0.020308&0.023929\\3&"LCVQE"&0.604743&0.54535&0.016667&0.016952&0.030307&0.023929\\2&"RDPM"&0.604743&0.54535&0.025&0.025321&0.040204&0.023929\\1&"COPKM"&0.604743&0.54535&0.05&0.05&0.05&0.05\\\hline
\end{tabular}
\caption{Post Hoc comparison Table for $\alpha=0.05$ (FRIEDMAN)}
\end{table}Holm's procedure rejects those hypotheses that have an unadjusted p-value $\le0.0125$.

Holland's procedure rejects those hypotheses that have an unadjusted p-value $\le0.012741$.

Finner's procedure rejects those hypotheses that have an unadjusted p-value $\le0.020308$.

Li's procedure rejects those hypotheses that have an unadjusted p-value $\le0.023929$.

@@

\begin{table}[!htp]
\centering\small
\begin{tabular}{cccc}
i&algorithm&unadjusted $p$&$p_{Holm}$\\
\hline1&"CEKM"&0.000135&0.000674\\2&"TVClust"&0.344704&1.378817\\3&"LCVQE"&0.54535&1.636049\\4&"RDPM"&0.54535&1.636049\\5&"COPKM"&0.54535&1.636049\\\hline
\end{tabular}
\caption{Adjusted $p$-values (FRIEDMAN) (I)}
\end{table}
\begin{table}[!htp]
\centering\small
\begin{tabular}{cccccc}
i&algorithm&unadjusted $p$&$p_{Holland}$&$p_{Finner}$&$p_{Li}$\\
\hline1&"CEKM"&0.000135&0.000674&0.000674&0.000296\\2&"TVClust"&0.344704&0.815605&0.652389&0.431228\\3&"LCVQE"&0.54535&0.906021&0.731179&0.54535\\4&"RDPM"&0.54535&0.906021&0.731179&0.54535\\5&"COPKM"&0.54535&0.906021&0.731179&0.54535\\\hline
\end{tabular}
\caption{Adjusted $p$-values (FRIEDMAN) (II)}
\end{table}

### 2019-03-23 Resultados/ResultadosTFG/Friedman/Friedman20/Friedman20.tex
Resultados de DILS completos

\begin{table}[!htp]
\centering
\begin{tabular}{|c|c|}\hline
Algorithm&Ranking\\\hline
"SHADE"&2.92\\"COPKM"&3.24\\"LCVQE"&3.24\\"RDPM"&3.24\\"TVClust"&3.42\\"CEKM"&4.94\\\hline\end{tabular}
\caption{Average Rankings of the algorithms (Friedman)}
\end{table}

Friedman statistic (distributed according to chi-square with 5 degrees of freedom): 18.708571. \newline P-value computed by Friedman Test: 0.002178.\newline

@@

\begin{table}[!htp]
\centering\footnotesize
\begin{tabular}{cccccccc}
$i$&algorithm&$z=(R_0 - R_i)/SE$&$p$&Holm &Holland&Finner&Li\\
\hline5&"CEKM"&3.817441&0.000135&0.01&0.010206&0.010206&0.023929\\4&"TVClust"&0.944911&0.344704&0.0125&0.012741&0.020308&0.023929\\3&"LCVQE"&0.604743&0.54535&0.016667&0.016952&0.030307&0.023929\\2&"RDPM"&0.604743&0.54535&0.025&0.025321&0.040204&0.023929\\1&"COPKM"&0.604743&0.54535&0.05&0.05&0.05&0.05\\\hline
\end{tabular}
\caption{Post Hoc comparison Table for $\alpha=0.05$ (FRIEDMAN)}
\end{table}Holm's procedure rejects those hypotheses that have an unadjusted p-value $\le0.0125$.

@@

Li's procedure rejects those hypotheses that have an unadjusted p-value $\le0.023929$.

@@

\begin{table}[!htp]
\centering\small
\begin{tabular}{cccc}
i&algorithm&unadjusted $p$&$p_{Holm}$\\
\hline1&"CEKM"&0.000135&0.000674\\2&"TVClust"&0.344704&1.378817\\3&"LCVQE"&0.54535&1.636049\\4&"RDPM"&0.54535&1.636049\\5&"COPKM"&0.54535&1.636049\\\hline
\end{tabular}
\caption{Adjusted $p$-values (FRIEDMAN) (I)}
\end{table}
\begin{table}[!htp]
\centering\small
\begin{tabular}{cccccc}
i&algorithm&unadjusted $p$&$p_{Holland}$&$p_{Finner}$&$p_{Li}$\\
\hline1&"CEKM"&0.000135&0.000674&0.000674&0.000296\\2&"TVClust"&0.344704&0.815605&0.652389&0.431228\\3&"LCVQE"&0.54535&0.906021&0.731179&0.54535\\4&"RDPM"&0.54535&0.906021&0.731179&0.54535\\5&"COPKM"&0.54535&0.906021&0.731179&0.54535\\\hline
\end{tabular}
\caption{Adjusted $p$-values (FRIEDMAN) (II)}
\end{table}

>>>>

\begin{table}[!htp]
\centering
\begin{tabular}{|c|c|}\hline
Algorithm&Ranking\\\hline
"SHADE"&2.8\\"COPKM"&2.86\\"LCVQE"&3.66\\"RDPM"&3.28\\"TVClust"&3.3\\"CEKM"&5.1\\\hline\end{tabular}
\caption{Average Rankings of the algorithms (Friedman)}
\end{table}

Friedman statistic (distributed according to chi-square with 5 degrees of freedom): 25.525714. \newline P-value computed by Friedman Test: 0.00011.\newline

@@

\begin{table}[!htp]
\centering\footnotesize
\begin{tabular}{cccccccc}
$i$&algorithm&$z=(R_0 - R_i)/SE$&$p$&Holm &Holland&Finner&Li\\
\hline5&"CEKM"&4.346591&0.000014&0.01&0.010206&0.010206&0.004751\\4&"LCVQE"&1.625247&0.10411&0.0125&0.012741&0.020308&0.004751\\3&"TVClust"&0.944911&0.344704&0.016667&0.016952&0.030307&0.004751\\2&"RDPM"&0.907115&0.364346&0.025&0.025321&0.040204&0.004751\\1&"COPKM"&0.113389&0.909722&0.05&0.05&0.05&0.05\\\hline
\end{tabular}
\caption{Post Hoc comparison Table for $\alpha=0.05$ (FRIEDMAN)}
\end{table}Holm's procedure rejects those hypotheses that have an unadjusted p-value $\le0.0125$.

@@

Li's procedure rejects those hypotheses that have an unadjusted p-value $\le0.004751$.

@@

\begin{table}[!htp]
\centering\small
\begin{tabular}{cccc}
i&algorithm&unadjusted $p$&$p_{Holm}$\\
\hline1&"CEKM"&0.000014&0.000069\\2&"LCVQE"&0.10411&0.41644\\3&"TVClust"&0.344704&1.034113\\4&"RDPM"&0.364346&1.034113\\5&"COPKM"&0.909722&1.034113\\\hline
\end{tabular}
\caption{Adjusted $p$-values (FRIEDMAN) (I)}
\end{table}
\begin{table}[!htp]
\centering\small
\begin{tabular}{cccccc}
i&algorithm&unadjusted $p$&$p_{Holland}$&$p_{Finner}$&$p_{Li}$\\
\hline1&"CEKM"&0.000014&0.000069&0.000069&0.000153\\2&"LCVQE"&0.10411&0.355803&0.240309&0.535578\\3&"TVClust"&0.344704&0.718608&0.505618&0.792456\\4&"RDPM"&0.364346&0.718608&0.505618&0.801423\\5&"COPKM"&0.909722&0.909722&0.909722&0.909722\\\hline
\end{tabular}
\caption{Adjusted $p$-values (FRIEDMAN) (II)}
\end{table}
